{\acronym} meets FOX: an ensemble approach to entity linking based on vector similarity

### 2015-08-20 paper.tex
- added a footnote with the url for the result download

We evaluate our entity linking approach on two datasets, AIDA/CoNLL and KORE50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}},  
in terms of precision and recall. Precision, recall, and the derived $F_1$ score were defined as follows:

>>>>

We evaluate our entity linking approach on two datasets\footnote{{\acronym}'s results for the 10-fold cross validations can be downloaded from: \url{http://sebastianwalter.org/weasel/nFoldresults.zip}}, AIDA/CoNLL and KORE50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}},  
in terms of precision and recall. Precision, recall, and the derived $F_1$ score were defined as follows:
